---
title: "Example code snippets"
author: Jacob Bradley
date: May 13, 2023
output: md_document
---
```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = here::here())
```

# Example usage of Edinburgh Airport queue simulation toolkit
In this workbook we'll introduce some of the code blocks building up our analysis. None of these are directly used to produce results seen in the report (these are incorporated into our `targets` workflow management) but hopefully will provide useful context if attempting to understand, use and adapt our codebase.

## Loading relevant libraries and code
Throughout most of our analysis we make use only of `tidyverse` ecosystem libraries, as well as `here` for working with paths within the project and `targets` for workflow management. We load these packages here, as well as the import bits of
``` {r, message = FALSE}
library(tidyverse)
library(here)
library(targets)

tar_source(files = c(
  here("code/process_data.R"), 
  here("code/step_1_aircraft.R"),
  here("code/step_2_route.R"),
  here("code/step_3_immigration.R"),
  here("code/kpis.R"),
  here("code/analysis.R"),
  here("code/get_figures.R"),
  here("code/get_tables.R")
))
```

## Example single simulation
Here we show how to produce a single simulation. Note that first we have to make sure `targets` has access to the right objects and datasets. We do this as follows (we'll explain more of what's going on here later).

``` {r, message = FALSE}
tar_make(c(
  'future_aircrafts_arrivals',
  'hubs',
  'countries',
  'prop_nationality',
  'delay_dist',
  'n_passengers_quantiles',
  'load_factor',
  'future_coached_levels',
  'coach_dist',
  'walk_dist',
  'base_walk_dist',
  'egate_failure_prop',
  'failed_egate_priority'
))
```

We now make some desks and eGates.
``` {r}
n_desks <- 9
desk_means <- rep(90, n_desks)
bordercheck_desks <- list(n_borderchecks = n_desks, 
                          bordercheck_means = desk_means,
                          bordercheck_sd = 14)

n_egates <- 10
bordercheck_egates = list(
  n_borderchecks = n_egates, 
  bordercheck_mean = 45,
  bordercheck_sd = 5)

```

Now we can simulate some arrivals
``` {r}
simulated_arrivals <- tar_read(future_aircrafts_arrivals) %>% 
  complete_aircrafts_arrivals(tar_read(hubs), tar_read(countries), tar_read(prop_nationality), 
                              tar_read(delay_dist), tar_read(n_passengers_quantiles), 
                              tar_read(load_factor), tar_read(future_coached_levels)) %>% 
  get_passengers_after_aircrafts() %>% 
  get_passengers_after_routes(tar_read(coach_dist), tar_read(walk_dist), tar_read(base_walk_dist))

```

``` {r}

simulated_queue <- simulated_arrivals %>% 
  immigration_queue(bordercheck_desks = bordercheck_desks, 
             bordercheck_egates = bordercheck_egates, 
             egate_uptake_prop = .7, target_eligibility = .8, 
             egate_failure_prop = tar_read(egate_failure_prop), 
             failed_egate_priority = tar_read(failed_egate_priority))  
```